%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[letterpaper]{article}
\usepackage{latexsym}
\usepackage{amsbsy}
\usepackage{graphicx}
\begin{document}
\noindent
\textbf{Use Case 2:  Request Archived Weather Data}\\
\textbf{Scope:  }Weather Station\\
\textbf{Level:  }User Goal\\
\textbf{Primary Actor:  }User\\
\textbf{Secondary Actor:  }Archiving System (Database)\\
\textbf{Scenario:  }Request Archived Dewpoint Data\\
\textbf{Related Use Cases:  }N/A\\
\textbf{Stakeholders and Interests:  }
\begin{itemize}
\item User:  Wants to retrieve archived dewpoint data.
\item Weather Services:  Wants to retrieive and compare archived
dewpoint data for the purpose of comparing to other weather
stations, and for accuracy of instrumentation and correction of
Weather Station placement if needed.
\item National Weather Service:  Wants archived spotter weather data.
\item Weather Scientists and Observers:  Wants to to observe archived
meteorological data in a given locale.
\end{itemize}
\textbf{Preconditions:  }The Weather Station has archived the
dewpoint data for the given time frame requested; the
archiving system is available for requested data retrieval.\\
\textbf{Success Guaranties (Postconditions):  }Archived dewpoint
data is retrieved from the archiving system, and returned to the
User.\\\\
\textbf{Main Success Scenario:  }\\\\
\begin{tabular}{|p{6cm}|p{6cm}|}\hline
\textbf{User} & \textbf{System}\\\hline
1. Request Archived Dewpoint Data at a given time in the
desired units (Metric, English, Absolute).&\\\hline
&2.  Queries the external archiving system for the dewpoint
data at the requested time.\\\hline
&3.  Presents the archived data to the User in the desired
Units.\\\hline
\end{tabular}\\\\
\textbf{Alternative Flows:  }\\
2a.  If the external archiving system is not available at the
requested time:\\
2a1. System alerts the user--with a possible reason as to
why.\\\\
2b.  If the external archiving system is not available:\\
2b1. System
will try another (redundant) archiving system to see if the data is
available in the redundant system--alerting the user of the issue and
indicating its search in another archiving system.\\
2b2.  System informs user if another archiving system is not
available.\\\\
2c.  If the no dewpoint data is available at the User requested
time:\\
\quad2c1. System alerts the User of the unavailability of the
requested dewpoint data.\\\\
\textbf{Special Requirements:  }Somehow we want the archiving systmes
to be ATOM(ic) to recover from a crash as best as possible.\\\\
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
